\bf Title here

### 2020-08-19 paper/paper.Rmd
rearranging Sec.4&5 to 4. diagnostics and 5. application

# Visual diagnostic system {#vis-diag}

@@

## Simulated data

@@

## Visual diagnostic plots {#vis-diag-plots}

Below we will present several examples of diagnosing different aspects of the projection pursuit optimisation. We will present:

1) static plots to explore the index value,

2) animated plots to explore the projection basis and,

3) a self-contained example to optimise a complex index function.

In the first two sections, we will first provide a toy example that is easy to grasp and then more examples that can help us to understand the algorithm and parameter choice. Remember the research question we raised earlier, the purpose of visual diagnostics is to understand:

The first question can be answered using a static plot with x-axis showing the progression of the optimisation and y-axis showing the value of the objective function. The second question can be addressed via visualising the rotating high dimensional space or its projection on the reduced 2D space. Thus animated visualisation is needed to perceive the optimisation path in the searching space.

<!-- [This seems to be a hard task to see the rotation of high dimensional space, but the way humans understand the dimension of a 3D object is either through rotating the physical 3D object or using shade and line type to annotate the 3D object in a paper or electronically. Thus we can do a similar rotation on the screen to precieve even higher dimension. there is likely to be a learning curve - remember when learning geometry in school, it takes a while to get used to see 3D cube on a paper].  -->

## Explore the value of objective function {#static}

### Searching points

#### Toy example: exploring searching points

### Interpolating points

#### A more complex example: Interruption

@@

### Polishing points

@@

#### Another example: Polish

@@

## Explore searching space {#animated}

### A toy example: understand different stage of search_geodesic

*Example: understand search_geodesic* [feel like this example is merely explaining search geodesic algorithm, so maybe introduce the animated plot here? xxx] `search_geodesic` is a two-stage ascending algorithm with four different stages in the search and a PCA plot useful to understand how the algorithm progresses and the relative position of each basis in the PCA projected 2D space. Starting from the start basis, a directional search is conducted in a narrow neighbourhood on five random directions. The best one is picked and a line search is then run on the geodesic direction to find the target basis. The starting and target bases are then interpolated. In the next iteration, the target basis becomes the current basis and then the procedures continues.

### A more complex example: Choosing the initial value for polishing parameter

@@

# Application {#application}
# Implementation: Ferrn package {#implementation}

>>>>

# Visual diagnostics{#vis-diag}

@@

## Plot definition

### Explore the value of objective function {#static}

#### Searching points

##### Toy example: exploring searching points

#### Interpolating points

##### Toy example

#### A toy example: understand different stage of search_geodesic

`search_geodesic` is a two-stage ascending algorithm with four different stages in the search and a PCA plot useful to understand how the algorithm progresses and the relative position of each basis in the PCA projected 2D space. Starting from the start basis, a directional search is conducted in a narrow neighbourhood on five random directions. The best one is picked and a line search is then run on the geodesic direction to find the target basis. The starting and target bases are then interpolated. In the next iteration, the target basis becomes the current basis and then the procedures continues.

# Application {#application}

Below we will present several examples of diagnosing different aspects of the projection pursuit optimisation. We will present more examples that can help us to understand the algorithm and parameter choice:

1) ...
2) ...
3) ...
4) ...

Remember the research question we raised earlier, the purpose of visual diagnostics is to understand:

(mention optim difficulties and split the simulated data section into the examples!!!)

@@

## A more complex example: Interruption

@@

## Another example: Polish

@@

---

@@

## A more complex example: Choosing the initial value for polishing parameter

@@

# Implementation: Ferrn package {#implementation}

### 2020-08-19 paper/paper.tex
rearranging Sec.4&5 to 4. diagnostics and 5. application

\hypertarget{vis-diag}{%
\section{Visual diagnostic system}\label{vis-diag}}

@@

\hypertarget{simulated-data}{%
\subsection{Simulated data}\label{simulated-data}}

@@

\hypertarget{vis-diag-plots}{%
\subsection{Visual diagnostic plots}\label{vis-diag-plots}}

Below we will present several examples of diagnosing different aspects
of the projection pursuit optimisation. We will present:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  static plots to explore the index value,
\item
  animated plots to explore the projection basis and,
\item
  a self-contained example to optimise a complex index function.
\end{enumerate}

In the first two sections, we will first provide a toy example that is
easy to grasp and then more examples that can help us to understand the
algorithm and parameter choice. Remember the research question we raised
earlier, the purpose of visual diagnostics is to understand:

The first question can be answered using a static plot with x-axis
showing the progression of the optimisation and y-axis showing the value
of the objective function. The second question can be addressed via
visualising the rotating high dimensional space or its projection on the
reduced 2D space. Thus animated visualisation is needed to perceive the
optimisation path in the searching space.

\hypertarget{static}{%
\subsection{Explore the value of objective function}\label{static}}

\hypertarget{searching-points}{%
\subsubsection{Searching points}\label{searching-points}}

\hypertarget{toy-example-exploring-searching-points}{%
\paragraph{Toy example: exploring searching
points}\label{toy-example-exploring-searching-points}}

\hypertarget{interpolating-points}{%
\subsubsection{Interpolating points}\label{interpolating-points}}

\hypertarget{a-more-complex-example-interruption}{%
\paragraph{A more complex example:
Interruption}\label{a-more-complex-example-interruption}}

@@

\hypertarget{polishing-points}{%
\subsubsection{Polishing points}\label{polishing-points}}

@@

\hypertarget{another-example-polish}{%
\paragraph{Another example: Polish}\label{another-example-polish}}

@@

\hypertarget{animated}{%
\subsection{Explore searching space}\label{animated}}

\hypertarget{a-toy-example-understand-different-stage-of-search_geodesic}{%
\subsubsection{A toy example: understand different stage of
search\_geodesic}\label{a-toy-example-understand-different-stage-of-search_geodesic}}

\emph{Example: understand search\_geodesic} {[}feel like this example is
merely explaining search geodesic algorithm, so maybe introduce the
animated plot here? xxx{]} \texttt{search\_geodesic} is a two-stage
ascending algorithm with four different stages in the search and a PCA
plot useful to understand how the algorithm progresses and the relative
position of each basis in the PCA projected 2D space. Starting from the
start basis, a directional search is conducted in a narrow neighbourhood
on five random directions. The best one is picked and a line search is
then run on the geodesic direction to find the target basis. The
starting and target bases are then interpolated. In the next iteration,
the target basis becomes the current basis and then the procedures
continues.

\hypertarget{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}{%
\subsubsection{A more complex example: Choosing the initial value for
polishing
parameter}\label{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}}

@@

>>>>

\hypertarget{vis-diag}{%
\section{Visual diagnostics}\label{vis-diag}}

@@

\hypertarget{plot-definition}{%
\subsection{Plot definition}\label{plot-definition}}

\hypertarget{static}{%
\subsubsection{Explore the value of objective function}\label{static}}

\hypertarget{searching-points}{%
\paragraph{Searching points}\label{searching-points}}

\hypertarget{toy-example-exploring-searching-points}{%
\subparagraph{Toy example: exploring searching
points}\label{toy-example-exploring-searching-points}}

\hypertarget{interpolating-points}{%
\paragraph{Interpolating points}\label{interpolating-points}}

\hypertarget{toy-example}{%
\subparagraph{Toy example}\label{toy-example}}

\hypertarget{a-toy-example-understand-different-stage-of-search_geodesic}{%
\paragraph{A toy example: understand different stage of
search\_geodesic}\label{a-toy-example-understand-different-stage-of-search_geodesic}}

\texttt{search\_geodesic} is a two-stage ascending algorithm with four
different stages in the search and a PCA plot useful to understand how
the algorithm progresses and the relative position of each basis in the
PCA projected 2D space. Starting from the start basis, a directional
search is conducted in a narrow neighbourhood on five random directions.
The best one is picked and a line search is then run on the geodesic
direction to find the target basis. The starting and target bases are
then interpolated. In the next iteration, the target basis becomes the
current basis and then the procedures continues.

Below we will present several examples of diagnosing different aspects
of the projection pursuit optimisation. We will present more examples
that can help us to understand the algorithm and parameter choice:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \ldots{}
\item
  \ldots{}
\item
  \ldots{}
\item
  \ldots{}
\end{enumerate}

Remember the research question we raised earlier, the purpose of visual
diagnostics is to understand:

(mention optim difficulties and split the simulated data section into
the examples!!!)

@@

\hypertarget{a-more-complex-example-interruption}{%
\subsection{A more complex example:
Interruption}\label{a-more-complex-example-interruption}}

@@

\hypertarget{another-example-polish}{%
\subsection{Another example: Polish}\label{another-example-polish}}

@@

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

@@

\hypertarget{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}{%
\subsection{A more complex example: Choosing the initial value for
polishing
parameter}\label{a-more-complex-example-choosing-the-initial-value-for-polishing-parameter}}

@@

\hypertarget{explore-searching-space-1}{%
\subsubsection{Explore searching
space}\label{explore-searching-space-1}}
